Baseline Drift Estimation for Air Quality Data Using Quantile Trend Filtering

### 2019-04-09 Manuscript/detrendify_aoas.tex
added comment to Halley.

We compare the ability of the methods to estimate the true quantiles of $y(t_i)-s(t_i)$  for $\tau \in \{0.01, 0.05, 0.1\}$ and calculate the RMSE (\Fig{peaks_rmse}). In this simulation study, our proposed method \texttt{detrend\_eBIC} method substantially outperforms the others. The \texttt{detrend\_Xing} method, which is the \texttt{detrend\_eBIC} method fit without the non-crossing constraints, performs similarly for larger quantiles and larger datasets. However, \texttt{detrend\_Xing} produces significantly worse estimates for more extreme quantiles ($\tau = 0.01$) and smaller data sets ($\tau = 0.05$ and $n = 500$). These results indicate that even when a single quantile is of interest, simultaneously fitting nearby quantiles and utilizing the non-crossing constraint can improve estimates when data is sparse by using information from nearby quantiles. The \texttt{qsreg} method is comparable to the \texttt{detrend\_eBIC} method on the smaller datasets, but its performance deteriorates as the data size grows. The \texttt{npqw} and \texttt{detrend\_valid} methods both perform poorly on this design.

>>>>

We compare the ability of the methods to estimate the true quantiles of $y(t_i)-s(t_i)$  for $\tau \in \{0.01, 0.05, 0.1\}$ and calculate the RMSE (\Fig{peaks_rmse}). In this simulation study, our proposed method \texttt{detrend\_eBIC} method substantially outperforms the others. The \texttt{detrend\_Xing} method, which is the \texttt{detrend\_eBIC} method fit without the non-crossing constraints, performs similarly for larger quantiles and larger datasets. However, \texttt{detrend\_Xing} produces significantly worse estimates for more extreme quantiles ($\tau = 0.01$) and smaller data sets ($\tau = 0.05$ and $n = 500$). These results indicate that even when a single quantile is of interest, simultaneously fitting nearby quantiles and utilizing the non-crossing constraint can improve estimates when data is sparse by using information from nearby quantiles. \Halley{Eric}{Should this be reversed? qsreg looks like it does as well as detrend-eBIC for large $n$ and worse for small $n$.}The \texttt{qsreg} method is comparable to the \texttt{detrend\_eBIC} method on the smaller datasets, but its performance deteriorates as the data size grows. The \texttt{npqw} and \texttt{detrend\_valid} methods both perform poorly on this design.
